---
title: "Seonggyu Park's CV"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [spark-cv.css]
    number_sections: false
links-to-footnotes: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(magrittr) # For the pipe 

source("cv_printing_functions.r")

opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

#### cv entries #####
cv_entries <- readxl::read_xlsx(here::here("data", "cv_entries.xlsx"))
research <- readxl::read_xlsx(here::here("data", "research.xlsx"))

#### publications #####
pubs <- readxl::read_xlsx(here::here("data", "pubs.xlsx")) %>% 
  arrange(order) %>% 
  select(-order)

pubs <- map_df(pubs, ~gsub("\\.$", "", .x))
courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))

```


```{r}
PDF <- FALSE # Set to TRUE when rendering to PDF via pagedown::chrome_print('spark-cv.Rmd', 'spark-cv.pdf')
if(PDF) {
  header <- '
  View online
  <a href="https://spark-brc.github.io/spark-cv/" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a>
  '
} else {
  header <- '
  Download PDF
  <a href="https://github.com/spark-brc/spark-brc.github.io/raw/master/spark-cv/spark-cv.pdf" class="icon-block">
      <i class="fas fafooter fa-download"></i>
  </a>
  '
}

```


<div class = "download">
```{r results = "asis"}
cat(header)
```
<div class = "footer",>
  <a href="https://github.com/spark-brc" class="icon-block">
      <i class="fab fafooter fa-github"> &ensp; | </i>
  </a>
  
  <a href="mailto:seonggyu.park@brc.tamus.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"> &ensp;| </i>
  </a>
  
  <a href="https://blackland.tamu.edu/people/research/scientists/park-seonggyu/" class="icon-block">
      <i class="fas fafooter fa-globe"> &ensp;| </i>
  </a>
  
  <a href="https://twitter.com/spark_brc" class="icon-block">
      <i class="fab fafooter fa-twitter"> &ensp;| </i>
  </a>
  
  <a href="https://scholar.google.com/citations?user=5Ob9lioAAAAJ&hl=en" class="icon-block">
      <i class="ai fafooter ai-google-scholar ai-lg"></i>
  </a>
  
</div>



</div>

<div id = "block_container">

<div class = "first", id="bloc1">Seonggyu</div>  
<div class = "last", id="bloc2">Park</div>

</div>

<div id = "block_container">
<div class = "first2", id="bloc1">Assistant Research</div>  
<div class = "last2", id="bloc2">Scientist</div>
</div>


<div id = "sub", class = "sub">
Curriculum Vita
</div>


<div class="grid-container">

```{r summary, child = here::here("content", "summary.Rmd")}
```

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>%
  mutate(
    loc = ifelse(!is.na(loc),
                paste0("<i class='fas location fa-map-marker-alt'></i>", loc),
                ""),
    what = paste0(what, ". ", where, ", ", loc),
    what = gsub("NA", "", what),
    what = gsub(", $", "", what),
    what = ifelse(!is.na(url), 
                paste0("[", what, "](", url, ")"), 
                what)
         ) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```
<br>

## Brief professional history {.history .nohead}

```{r}
cv_entries %>% 
  filter(type == 'history') %>% 
  mutate(
    loc = ifelse(!is.na(loc),
                paste0("<i class='fas location fa-map-marker-alt'></i>", loc),
                ""),    
    what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where, ", ", loc),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()

```
<br class="pageBreak"/>

# Research Experience
<div class = "inote">
Icons link to additional content  
</div>

## Model Applications {.nohead .tch}

```{r}
research %>% 
  filter(type == "mp") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                          paste0( '<a href=', 
                                  website, 
                                  '><i class="fas falink fa-globe"></i></a>'),
                          ""),
          fa_git = ifelse(!is.na(repo), 
                          paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                          ""),
          fa_youtube = ifelse(!is.na(youtube), 
                          paste0('<a href=', 
                                youtube, 
                                '><i class="fas falink fa-youtube"></i></a>'),
                          ""),
          tool = ifelse(!is.na(tool),
                        paste0(
                          "<span class='background'>",
                          tool,
                          "</span>"
                          ),
                          ""),         
          year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "current", year_end)),
          what = paste0(what, ", ", "(",  year, "). ", tool, 
                          fa_git, fa_web, fa_youtube),
          what = gsub("NA, ", "", what),
          order = paste0(order, ".")
          ) %>% 
  select(point, what) %>% 
  kable()
```


## Model Development {.nohead .tch}

```{r}
research %>% 
  filter(type == "md") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                          paste0( '<a href=', 
                                  website, 
                                  '><i class="fas falink fa-globe"></i></a>'),
                          ""),
          fa_git = ifelse(!is.na(repo), 
                          paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                          ""),
          fa_youtube = ifelse(!is.na(youtube), 
                          paste0('<a href=', 
                                youtube, 
                                '><i class="fab fa-youtube"></i></a>'),
                          ""),
          product = ifelse(!is.na(product),
                        paste0(
                          "<span class='pbackground'>",
                          product,
                          "</span>"
                          ),
                          ""), 
          tool = ifelse(!is.na(tool),
                        paste0(
                          "<span class='background'>",
                          tool,
                          "</span>"
                          ),
                          ""),
          # year = str_c(year_begin, 
          #             " --- ", 
          #             ifelse(is.na(year_end), "current", year_end)),
          year = str_c(
                      ifelse(is.na(year_end), paste0(year_begin, "---", "current"), year_end)),
          what = paste0(what, ", ", "(",  year, "). ", product, ", ", tool, 
                          fa_git, fa_web, fa_youtube),
          what = gsub("NA, ", "", what),
          order = paste0(order, ".")
          ) %>% 
  select(point, what) %>% 
  kable()
```

## Software Development {.nohead .tch}

```{r}
  research %>% 
  filter(type == "sd") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                          paste0( '<a href=', 
                                  website, 
                                  '><i class="fas falink fa-globe"></i></a>'),
                          ""),
          fa_git = ifelse(!is.na(repo), 
                          paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                          ""),
          fa_youtube = ifelse(!is.na(youtube), 
                          paste0('<a href=', 
                                youtube, 
                                '><i class="fab falink fa-youtube"></i></a>'),
                          ""),
          product = ifelse(!is.na(product),
                        paste0(
                          "<span class='pbackground'>",
                          product,
                          "</span>"
                          ),
                          ""), 
          tool = ifelse(!is.na(tool),
                        paste0(
                          "<span class='background'>",
                          tool,
                          "</span>"
                          ),
                          ""),
          year = str_c(
                      ifelse(is.na(year_end), paste0(year_begin, "---", "current"), year_end)),
          what = paste0(what, ", ", "(",  year, "). ", product, ", ", tool, 
                          fa_git, fa_web, fa_youtube),
          what = gsub("NA, ", "", what),
          order = paste0(order, ".")
          ) %>% 
  select(point, what) %>% 
  kable()
# <br class="pageBreak"/>
```


## Web applications {.nohead .tch}
```{r}
  research %>% 
  filter(type == "wa") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                          paste0( '<a href=', 
                                  website, 
                                  '><i class="fas falink fa-globe"></i></a>'),
                          ""),
          fa_git = ifelse(!is.na(repo), 
                          paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                          ""),
          fa_youtube = ifelse(!is.na(youtube), 
                          paste0('<a href=', 
                                youtube, 
                                '><i class="fab falink fa-youtube"></i></a>'),
                          ""),
          tool = ifelse(!is.na(tool),
                        paste0(
                          # "<span style='background-color:#a3c4da; color:white;border-radius:4px; padding-right:2px;padding-left:2px;'>"
                          "<span class='background'>",
                          tool,
                          "</span>"
                          ),
                          ""),
          year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "current", year_end)),
          what = paste0(what, ". ", "(",  year, "). ", tool, 
                          fa_git, fa_web, fa_youtube),
          what = gsub("NA, ", "", what),
          order = paste0(order, ".")
          ) %>% 
  select(point, what) %>% 
  kable()
```
<br>

## Peer-Reviewed Publications

```{r}
make_cite <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL,
                      version = NULL,...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), " (", issue,"),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0('[<i class="ai location ai-doi ai-lg"></i>',doi,'](',url, ')')
    # doi <- paste0('[<i class="ai ai-doi ai-lg"></i>',doi,'](',url, ')')
  }

  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(annual_meeting) {
       conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ",", 
                            "<i class='fas location fa-map-marker-alt'></i>",                             
                            # "<span style='color:#a3c3d9;margin-left:1.5em;margin-right:-0.5em'><i class='fas fa-map-marker-alt'></i></span>", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                            ",", 
                            "<i class='fas location fa-map-marker-alt'></i>",
                            conf_loc,
                            ".") 
      }
    }
    else {
       if(annual_meeting) {
          conference <- paste0("at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            "<i class='fas location fa-map-marker-alt'></i>",
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0(
                            "at the ", 
                            conference,
                            ",",
                            "<i class='fas location fa-map-marker-alt'></i>",
                            conf_loc,
                            ".") 
      }
    }

  }
  if(!is.null(version)) {
    version <- paste0("R package version ", version, ".")
  }
  authors <- gsub(
    "Park, S\\.?",
    "<span style= 'font-weight: 500'>Park, S.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, ", "),
        version, 
        conference,
        journal, 
        volume,
        book,
        pages, 
        doi,
        place_published)
}

prpas <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prpas, seq_len(nrow(prpas)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prpas$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prpas$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prpas$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prpas$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prpas$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)
```

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl[1:6, ])
```

</div>

<br class="pageBreak"/>

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl[7:nrow(pubs_tbl), ])
```

</div>


## Manuscripts under review for publication {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "in-review") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 
  
  kable(submitted_tbl) 
}
```

</div>
<!-- <br class="pageBreak"/> -->

## Training Manuals {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "manual") %>% 
  select(-type)

fa_web = ifelse(
  !is.na(submitted$url), 
  paste0(
    '[<i class="fas falink fa-globe"></i>](',
    submitted$url,
    ")"),
    "")

# falink makes gray
fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_web, fa_doc, fa_git)) 
  
  kable(submitted_tbl) 
}
```

</div>


## Technical Reports {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "technical_report") %>% 
  select(-type)

fa_web = ifelse(
  !is.na(submitted$url), 
  paste0(
    '[<i class="fas falink fa-globe"></i>](',
    submitted$url,
    ")"),
    "")

# falink makes gray
fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_web, fa_doc, fa_git)) 
  
  kable(submitted_tbl) 
}
```

</div>

## National & International Conference Presentations {.prpa .nohead}

<div class = "hangingindent">

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_youtube = ifelse(!is.na(confs$youtube), 
                paste0('<a href=', 
                      confs$youtube, 
                      '><i class="fab falink fa-youtube"></i></a>'),
                "")

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )

each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git,
                                 fa_youtube)
)
  

conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

kable(conf_tbl[1:4, ])
```

</div>

<br class="pageBreak">


<div class = "hangingindent prpa nohead">

```{r}
kable(conf_tbl[5:15, ])
```

</div>

<br class="pageBreak">
<div class = "hangingindent prpa nohead">

```{r}
kable(conf_tbl[16:nrow(conf_tbl), ])
```

</div>
<br class="pageBreak">


# Funding Activity

<div class = "inote">
Icons link to additional content
</div>

```{r}
grants <- readxl::read_xlsx(here::here("data", "grants.xlsx"))

make_grant_cite <- function(title, funding_agency, award_num, role, pi,
  date_start, date_end, budget, fte_low_range, fte_high_range, contract,
  link, in_review = FALSE, ...) {

  if(in_review) {
    budg <- paste0(". Proposed budget: $",
                   prettyNum(budget, big.mark = ",")
                   )
  } else {
    budg <- paste0(". Total budget: $",
                    prettyNum(budget, big.mark = ",")
                    )
  }
  funder <- paste0("*", funding_agency, "* ")
  if(!is.na(award_num)) {
    funder <- paste0(funder, " (Award #", award_num, ")")
  }
  if(fte_low_range != fte_high_range) {
    fte <- paste0("FTE: ",
                  format(fte_low_range, nsmall = 2),
                  " to ",
                  format(fte_high_range, nsmall = 2),
                  " across project years.")
  }
  else {
    fte <- paste0("FTE: ", format(fte_low_range, nsmall = 2), ".")
  }

  cite <- paste0(paste0(title, ". "),
                 paste(month(date_start, label = TRUE, abbr = FALSE),
                       year(date_start),
                       "to",
                       month(date_end, label = TRUE, abbr = FALSE),
                       year(date_end)),
                 ". ", funder,
                 budg,
                 paste0(". ",
                        "<span style= 'font-weight: 500'> Role: </span>",
                        role,
                        ". ")
                )
  cite <- ifelse(!is.na(pi),
                 paste0(cite, " PI: ", pi, "."),
                 cite)
  icon <- ifelse(!is.na(link),
                 paste('<a href=',
                       link,
                       '><i class="fas falink2 fa-globe"></i></a>'),
                 "")
  paste(cite, fte, icon)
}
```

## Under review {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants_submitted <- grants %>%
  filter(type == "in-review") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite)

kable(grants_submitted[1:2, ])
```

</div>

<!-- <br class = "pageBreak"/> -->

## Current projects {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants %>%
  filter(type == "current") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite) %>%
  kable()
```

</div>


<!-- ## Completed projects {.nohead .submitted} -->

<!-- <div class = "hangingindent"> -->

<!-- ```{r} -->
<!-- grants %>% -->
<!--   filter(type == "completed") %>% -->
<!--   group_by(count = paste0(seq(1, nrow(.)), ".")) %>% -->
<!--   nest() %>% -->
<!--   mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>% -->
<!--   select(-data) %>% -->
<!--   unnest(cite) %>% -->
<!--   kable() -->
<!-- ``` -->

<!-- </div> -->

<!-- <br class = "pageBreak"/> -->

<!-- ## Submitted (unfunded) {.nohead .submitted} -->

<!-- Only applications submitted as Principal Investigator to national agencies are displayed. -->


<!-- ```{r} -->
<!-- rejected <- grants %>% -->
<!--   filter(type == "rejected") %>% -->
<!--   group_by(count = paste0(seq(1, nrow(.)), ".")) %>% -->
<!--   nest() %>% -->
<!--   mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>% -->
<!--   select(-data) %>% -->
<!--   unnest(cite) -->
<!-- ``` -->

<!-- <div class = "hangingindent"> -->
<!-- ```{r } -->
<!-- kable(rejected) -->
<!-- ``` -->
<!-- </div> -->


# Professional Service 
## Workshops delivered{.nohead .submitted}

<div class = "hangingindent">

```{r}
workshops <- cv_entries %>%
  filter(type == "workshop-delivered")

workshops %>%
  mutate(
    loc = ifelse(!is.na(loc),
                paste0("<i class='fas location fa-map-marker-alt'></i>", loc),
                ""),
    pps = ifelse(!is.na(participants),
                paste0("<i class='fas location fa-users'></i>", " number of attendees: ", participants),
                ""),

    count = paste0(seq(nrow(.), 1), "."),
          cite = paste0(paste0(what, ", ", pps), 
                        ", (", 
                        year_end, 
                        "). ",
                        paste0("*", where, "*"), ",", loc, ".")) %>%
  select(count, cite) %>%
  kable()
```

</div>

## Invited talks{.nohead .submitted}
<div class = "hangingindent">

```{r}
talks <- cv_entries %>%
  filter(type == "invited-talks")

talks %>%
  mutate(
    loc = ifelse(!is.na(loc),
                paste0("<i class='fas location fa-map-marker-alt'></i>", loc),
                ""),    
    
    count = paste0(seq(nrow(.), 1), "."),
          cite = paste0(paste0(what),
                        ", (", 
                        year_end, 
                        "). ",
                        paste0("*", where, "*"), ",", loc, ".")) %>%
  select(count, cite) %>%
  kable()
```
</div>

<br class="pageBreak">

# Fellowships & Awards {.submitted .nohead}

<div class = "hangingindent">

```{r}
cv_entries %>%
  filter(type == "award") %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(what, ", ", where,  ", ", (ifelse(!is.na(additional_info), 
                              paste0("$", additional_info, ","),
                              "")), " (", year_end, "). ")
        ) %>%
  select(count, cite) %>%
  kable()
```
</div>

<br>

# Professional Affiliations {.nohead .submitted}

<div class="hangingindent">

```{r}
cv_entries %>%
  filter(type == "affiliation") %>%
  mutate(count = paste0(seq(nrow(.), 1), ".")) %>%
  select(count, what) %>%
  kable()
```
</div>



# Teaching

<div class = "inote">
Icons link to additional content  
</div>

## Related experience{.nohead .tch}

```{r}
research %>% 
  filter(type == "teaching") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                          paste0( '<a href=', 
                                  website, 
                                  '><i class="fas falink fa-globe"></i></a>'),
                          ""),
          fa_git = ifelse(!is.na(repo), 
                          paste0('<a href=', 
                                repo, 
                                '><i class="fab falink fa-github"></i></a>'),
                          ""),
          fa_youtube = ifelse(!is.na(youtube), 
                          paste0('<a href=', 
                                youtube, 
                                '><i class="fab fa-youtube"></i></a>'),
                          ""),
          tool = ifelse(!is.na(tool),
                        paste0(
                          "<i class='background'>",
                          tool,
                          "</i>"
                          ),
                          ""),
          year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "current", year_end)),
          what = paste0(what, ". ", "(",  year, "). ", tool, 
                          fa_git, fa_web, fa_youtube),
          what = gsub("NA, ", "", what),
          order = paste0(order, ".")
          ) %>% 
  select(point, what) %>% 
  kable()
```
